Multisensor Architecture for an Intersection Management System

### 2018-07-31 ch3-arch_sys.tex
Ch5 ok. Update.

\item[clusters\_vehicle\_counter] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
\caption{clusters\_vehicle\_counter}
\label{clusters_vehicle_counter}
\end{figure}

@@

\item[occgrid\_vehicle\_counter] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
\caption{occgrid\_vehicle\_counter}
\label{occgrid_vehicle_counter}
\end{figure}

@@

>>>>

\item[vehicle\_counter] \hfill

\begin{figure}[ht!]
\centering
\includegraphics[scale=1]{fig/3/clusters_veh_counter.pdf}
\caption{Vehicle\_counter}
\label{vehicle_counter}
\end{figure}

\todo{CHANGE FIGURE}

This block accepts different types of inputs, cluster\_msg and occgrid\_msg. It process the incoming data, and generate bounding boxes based on the clusters or based on the occupancy grid, according to the input. Having these bounding boxes, which represent detected vehicles, scene configuration data is loaded and the geometric parameters of the legs and lanes are used to generate virtual sensors at the entry and exit points of the intersection and check the overlaping of detected vehicles with aforemetioned virtual sensors.

This detection is made in a frame basis, meaning that if the overlaping area of a virtual sensor is greater than a threshold $ov_{th}$, it is considered that there is a vehicle over the sensor in that frame. Thus, the vehicle counter $v_{cnt}$ is incremented by one when a transition from occupied state to empty state is detected in a new frame.

@@

%\item[occgrid\_vehicle\_counter] \hfill
%
%\begin{figure}[ht!]
%\centering
%\includegraphics[scale=1]{fig/3/occgrid_veh_counter.pdf}
%\caption{occgrid\_vehicle\_counter}
%\label{occgrid_vehicle_counter}
%\end{figure}

@@

A whole intersection management system contains many different components, for example the instrumentation of the junction, the handling of data and information, the control policies and requirements, and the interaction between those elements. None of these items is more relevant than the others and it is for this reason that each one of them should be well conceived having in mind a common framework that allows their scalability, modularity and reliability. When these three features are accomplished, a change or an upgrade of any part of the system will not affect the remaining ones.

It is also important that an Intersection Management System should be flexible, not tied to one deployment or scenario, but also that allows to perform tests over new datasets or junctions, at no extra cost or just with some configuration adjustments. Although it is hard to have a one-rules-them-all system due to the variety of intersections (crossroads with different numbers of legs, roundabouts, T-shaped, Y-shaped, etc.), there are common needs, features and requirements that makes relevant to use an interesection management system looking forward to monitor, control and improve safety and efficiency in transportation.

### 2018-07-31 ch4-results.tex
Ch5 ok. Update.

@@

The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}). It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated manually.

@@

\subsection{Case 2: Multiple Lasers}

@@

\subsection{Results and Comparison}

>>>>

\epigraph{"Testing leads to failure, and failure leads to understanding"}{Burt Rutan}

In this chapter is presented the experimental setup used to deploy and test the proposed architecture. First is described the data and hardware and software specifications. Then, the two implemented configurations of the system are presented and finally, results are summarized and analysed.

@@

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.8]{fig/4/intersection-config2.pdf}
\caption{Possi dataset configuration}
\label{possi_img}
\end{figure}

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.2]{fig/4/sensors_overview.jpeg}
\caption{Overview of sensors data. Left: Laser scanners, Right: Camera.}
\label{possi_sensors}
\end{figure}

%\subsection{Data}
The selected dataset for testing the system is the one from POSSi project (section \ref{possi_ds}). It contains 6 laser-scanners raw readings and a video from a camera located over the intersection. Figure \ref{possi_img} depicts the configuration used by this dataset. In figure \ref{possi_sensors} is shown the data from each type of sensors, laser scanners and camera. The ground truth data used for validation is the vehicle count over 3 of the 5 legs of the intersection, taking into account the time at which a vehicle appears. This groundtruth data was generated manually.

%\subsection{Hardware and software specifications}

The platform used for the implementation is a laptop ASUS GL552VW, with 8GB RAM DDR4, a processor Intel Core i7 6700HQ @ 2.60GHz x 8 cores and graphic card Nvidia GeForce GTX 960M. The operating systems running on it is Ubuntu 16.04 LTS. The software was developed using primarily Python3 and C++ as programming languages. Used libraries are MatplotLib, Scikit, Numpy, OpenCV, and darknet for data processing and visualisation. For communication scheme redis was installed along some JSON parsers for formatting.

@@

\subsection{Case 2: Camera and Multiple Lasers}

@@

\section{Results}

\subsection{Case 1: Single camera}

Detection results in three diferent frames are shown in figure \ref{camera_detection}.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.115]{fig/4/camera.jpeg}
\caption{Vehicle detection using camera}
\label{camera_detection}
\end{figure}

\subsection{Case 2: Camera and multple lasers}

Vehicle detection based on laser scanners is shown in figure \ref{laser_detection}.

\begin{figure}[ht!]
\centering
\includegraphics[scale=0.43]{fig/4/laser1.png}
\caption{Vehicle detection using laser scanners}
\label{laser_detection}
\end{figure}

\section{Conclusions}

### 2018-07-31 ch5-conclusions.tex
Ch5 ok. Update.

\section{General Conclusions}

@@

Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, it is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.

@@

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is for architecture description and example implementation and another for application comparison.

>>>>

%\section{General Conclusions}

@@

Intersection monitoring is an active need in the purpose of improve traffic performance, and the option to measure its current state in an automated and intelligent way, is of great interest for local authorities and governments in order to develop policies and control schemes on short, mid or long-term basis.

@@

On the other side, a couple of articles are being reviewed previous to be submmited to a journal. One article is  a review on intersection management systems, based on chapter 1 and another for architecture description and example implementation , based on chapters 2 and 3.
